Tor's Usability for Censorship Circumvention

### 2015-10-09 paper/circumvention-experiment.tex
added thorough captions to the configuration window figures

\begin{figure}[h]
\label{fig:window1}
  \centering
    \includegraphics[width=0.5\textwidth]{window1.png}
    \caption{window1}
\end{figure}

\begin{figure}[h]
\label{fig:window2}
  \centering
    \includegraphics[width=0.5\textwidth]{window2.png}
    \caption{window2}
\end{figure}

\begin{figure}[h]
\label{fig:window3}
  \centering
    \includegraphics[width=0.5\textwidth]{window3.png}
    \caption{window3}
\end{figure}

\begin{figure}[h]
\label{fig:window4}
  \centering
    \includegraphics[width=0.5\textwidth]{window4.png}
    \caption{window4}
\end{figure}

\begin{figure}[h]
\label{fig:window5}
  \centering
    \includegraphics[width=0.5\textwidth]{window5.png}
    \caption{window5}
\end{figure}
\end{document}

>>>>

\begin{figure}[h]
\label{fig:window1}
  \centering
    \includegraphics[width=0.5\textwidth]{window1.png}
    \caption{Window 1: the first configuration window shown to the user upon
    starting Tor Browser for the first time. Note that the interface's default choice
    is to connect directly through Tor. The interface also gives additional guidance
    to help users answer this question.}
\end{figure}

\begin{figure}[h]
\label{fig:window2}
  \centering
    \includegraphics[width=0.5\textwidth]{window2.png}
    \caption{Window 2: This is the next window shown if a user chooses to configure 
    bridges or proxies. Note that the interface's default answer is ``No,'' 
    and also advises users to click ``No'' if they are unsure. The user can navigate to the 
    previous window by clicking ``Go Back,'' and continue configuration by clicking 
    ``Continue.''}
\end{figure}

\begin{figure}[h]
\label{fig:window3}
  \centering
    \includegraphics[width=0.5\textwidth]{window3.png}
    \caption{Window 3: This is the window shown when a user answers that a bridge 
    is required for the connection. Note that the default answer is to connect with a hard-
    coded bridge rather than to enter in a custom bridge, and to use the recommended 
    transport (obfs3). A possible source of confusion is that that the user is asked to choose 
    a transport type, when the interface clearly is asking for bridge configuration. The user 
    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
    by clicking  ``Continue.''}
\end{figure}

\begin{figure}[h]
\label{fig:window4}
  \centering
    \includegraphics[width=0.5\textwidth]{window4.png}
    \caption{Window 4: This is the window shown after a user has deemed that a bridge
    is not required for the connection, or when the bridge configuration settings have been 
    chosen. Note that the default answer to if the user requires a proxy is ``No.'' Additionally,
    there is text to guide the users on how to answer this question. The user 
    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
    by clicking  ``Continue.''}
\end{figure}

\begin{figure}[h]
\label{fig:window5}
  \centering
    \includegraphics[width=0.5\textwidth]{window5.png}
    \caption{Window 5: This is the window shown when a user answers that a proxy is 
    required for the connection. Note that there are no default values in the answers, 
    where there were for bridges. Additionally, since this is the last window in the configuration
    interface, the options to navigate to other windows are to simply ``go back,'' or to 
    connect to the Tor Network.}
\end{figure}
\end{document}
